### 2021-04-09 submission/manuscript.tex
Fix titlepage superscripts

Sarah Tomkovich\^{}1, Ana Taylor, Jacob King, Joanna Colovas, Lucas
Bishop, Kathryn McBride, Sonya Royzenblat, Nicholas A. Lesniak, Ingrid
L. Bergin\^{}2, Patrick D. Schloss\textsuperscript{1\(\dagger\)}\$

>>>>

Sarah Tomkovich\textsuperscript{1}, Ana Taylor\textsuperscript{1}, Jacob
King\textsuperscript{1}, Joanna Colovas\textsuperscript{1}, Lucas
Bishop\textsuperscript{1}, Kathryn McBride\textsuperscript{1}, Sonya
Royzenblat\textsuperscript{1}, Nicholas A. Lesniak\textsuperscript{1},
Ingrid L. Bergin\textsuperscript{2}, Patrick D.
Schloss\textsuperscript{1\(\dagger\)}
